%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMP 1805
% December 9 2011
% Review questions
% Problems mostly taken from Rosen 6th, typed up by Simon Pratt
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}
\usepackage{enumitem}

\begin{document}

{\Huge COMP 1805 Review Questions}

From Rosen (6th ed.)

1.1: 33e) Construct a truth table for:

\[
(p \leftrightarrow q) \vee (\neg q \leftrightarrow r)
\]

1.2: 30) Show that the following is a tautology:

\[
(p \vee q) \wedge (\neg p \vee r) \rightarrow (q \vee r)
\]

1.4: 33) Rewrite each of these statements so that negations appear only within predicates:

\begin{enumerate}[label=\alph{enumi})]
\item $ \neg \forall x \forall y P(x,y) $
\item $ \neg \forall y \exists x P(x,y) $
\item $ \neg \forall y \forall x (P(x,y) \vee Q(x,y)) $
\item $ \neg ( \exists x \exists y \neg P(x,y) \wedge \forall x \forall y Q(x,y)) $
\item $ \neg \forall x ( \exists y \forall z P(x,y,z) \wedge \exists z \forall y P(x,y,z)) $
\end{enumerate}

1.6: 39) Prove that at least one of the real numbers $a_1,a_2,...,a_n$ is greater than or equal to the average of these numbers.

1.6: 40) Use Exercise 39 to show that if the first 10 positive integers are placed around a circle, in any order, there exist three integers in consecutive locations around the circle that have a sum greater than or equal to 17.

1.7: 32) Prove that $\sqrt[3]{2}$ is irrational.

2.1: 19c) Find the power set of $ \{ \emptyset , \{ \emptyset \} \} $

2.4: 31) Determine whether each of these sets is countable or uncountable.  For those that are countable, exhibit a one-to-one correspondence between the set of natural numbers and that set.

\begin{enumerate}[label=\alph{enumi})]
\item the negative integers
\item the even integers
\item the real numbers between 0 and $1/2$
\item integers that are multiples of 7
\end{enumerate}

3.2: 24)

\begin{enumerate}[label=\alph{enumi})]
\item Show that $3x + 7$ is $\Theta (x)$
\item Show that $2x^2+x-7$ is $\Theta (x^2)$
\item Show that $\lfloor x + 1/2 \rfloor$ is $\Theta (x)$
\item Show that $log(x^2+1)$ is $\Theta (log_2(x))$
\item Show that $log_{10}x$ is $\Theta (log_2(x))$
\end{enumerate}

4.1: 21) Prove that $2^n > n^2$ if $n$ is an integer greater than 4

4.1: 31) Prove that 2 divides $n^2 + n$ whenever $n$ is a positive integer

4.3: 13) Where $f_n$ is the $n$th Fibonacci number, prove that

\[
f_1 + f_3 + ... + f_{2n-1} = f_{2n}
\]

5.1: 31) How many strings of eight English letters are there

\begin{enumerate}[label=\alph{enumi})]
\item that contain no vowels, if letters can be repeated?
\item that contain no vowels, if letters cannot be repeated?
\item that start with a vowel, if letters can be repeated?
\item that start with a vowel, if letters cannot be repeated?
\item that contain at least one vowel, if letters can be repeated?
\item that contain exactly one vowel, if letters can be repeated?
\item that start with X and contain at least one vowel, if letters can be repeated?
\item that start and end with X and contain at least one vowel, if
  letters can be repeated?
\end{enumerate}

5.2: 9(modified) what is the minimum number of students, each of whom
comes from one of the 13 provinces and territories, who must be
enrolled in a university to guarantee that there are at least 100 who
come from the same province or territory?

5.2: 15) How many numbers must be selected from the set
$\{1,2,3,4,5,6\}$ to guarantee that at least one pair of these numbers
add up to 7?

5.3: 38) How many ways are there to select 12 countries in the United
Nations to serve on a council if 3 are selected from a block of 45, 4
are selected from a block of 57, and the others are selected from the
remaining 69 countries?

5.4: 9) What is the coefficient of $x^{101}y^{99}$ in the expansion of
$(2x-3y)^{200}$?

5.5: 11) How many ways are there to choose eight coins from a piggy
bank containing 100 identical pennies and 80 identical nickels?

8.1: 4) Determine whether the relation $R$ on the set of all people is reflexive, symmetric, antisymmetric, and/or transitive, where $(a,b) \in R$ if and only if

\begin{enumerate}[label=\alph{enumi})]
\item $a$ is taller than $b$
\item $a$ and $b$ were born on the same day
\item $a$ has the same first name as $b$
\item $a$ and $b$ have a common grandparent
\end{enumerate}

9.1: 12) Let $G$ be an undirected graph with a loop at every vertex.  Show that the relation $R$ on the set of vertices of $G$ such that $uRv$ if and only if there is an edge associated to $\{u,v\}$ is a symmetric, reflexive relation on $G$.

9.2: 6) Show that the sum, over the set of people at a party, of the number of people a person has shaken hands with, is even.  Assume that no one shakes their own hand.

9.7: 1) Can five houses be connected to two utilities without connections crossing?

\end{document}
